Hypertension and microbiome

### 2019-04-29 articletwo.Rmd
Ready?

```{r maaslin}
maas.results.df.signf <- maaslin$genus %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  Feature = gsub("_Bacteria", "", Feature),
                  beta = Coefficient) %>%
    dplyr::filter(Qval < 0.05) %>%
    arrange(Feature)

maaslinplot <- plot_maaslin_heatmap_final(maas.results.df.signf %>% dplyr::filter(Variable!="HYPERTENSION"),
                      beta.maxabs=max(abs(maas.results.df.signf[,'beta'])),
                      order.by.category=FALSE)

@@

```{r Write figure 3}
fig3head <- ""
fig3foot <- ""
writeimage(doc, 3, "cache/maaslin.png", fig3head, fig3foot)
```

>>>>

```{r maaslin}
maas.results.df.signf <- maaslin$genus %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  Feature = gsub("_Bacteria", "", Feature),
                  beta = Coefficient) %>%
    dplyr::filter(Qval < 0.05, Variable != "HYPERTENSION") %>%
    arrange(Feature)

my.plot.order <- function(x) {
    y <- seq(length(x))
    y[x == "Mean arterial pressure"] = 4
    y[x == "Systolic BP"] = 3
    y[x == "Diastolic BP"] = 2
    y[x == "Pulse pressure"] = 1
    y
}

maas.all.pairs <- expand.grid(Feature = maas.results.df.signf %>% pull(Feature),
                         Name = maas.results.df.signf %>% pull(Name))
maas.tables.df <- merge(maas.results.df.signf,
                   all.pairs,
                   all.y=TRUE,
                   by.y=c('Feature', 'Name'),
                   by.x=c('Feature', 'Name'))

maaslinplot <- ggplot(maas.tables.df, aes(x = Feature, y = reorder(Name, my.plot.order(Name)), fill = beta)) +
    geom_tile(aes(fill = 1)) +
    geom_tile(colour="white", size=0.25) +
    scale_fill_distiller(palette = "RdBu", name = "Effect size",
                         limits=c(-0.003, 0.003), breaks = c(-0.003, 0, 0.003), na.value="grey30") +
    coord_fixed() +
    xlab("") +
    ylab("") +
    theme_classic(10) +  
    theme(axis.text.x = element_text(angle = 90, hjust = 1.0, vjust=0.5, size=7),
          axis.text.y = element_text(size=7))

@@

```{r Write figure 3}
fig3head <- "Associations between genus level abundances and blood pressure variables"
fig3foot <- "Only backteria with significant associations are shown. Blood pressure variables are normalized and abundances are arcsin-square root transformed. Dark gray color represents unsignificant associations."
writeimage(doc, 3, "cache/maaslin.png", fig3head, fig3foot)
```
